---
title: "Blog"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: cosmo
---


# Mapping Twitter tweets

Start with downloading [ImageMagick](http://ftp.icm.edu.pl/packages/ImageMagick/binaries/) (ImageMagick-6.9.3-9-Q16-x64-dll.exe)

Then load the necessary packages:

```{r message = FALSE}
#install.packages(c("devtools", "rjson", "bit64", "httr"))
#install_github("geoffjentry/twitteR")
#install.packages("ROAuth")
#devtools::install_github("dgrtwo/gganimate").

library(twitteR)
library(ROAuth)
library(leaflet) 
library(maps)
library(ggmap)
library(dplyr)
library(DT)
library(tidyr)
library(maps)
library(purrr)
library(ggplot2)
library(ggthemes)
```


Get [Google API key](https://developers.google.com/maps/documentation/javascript/get-api-key)

```{r}
register_google(key = "ENTER YOUR KEY HERE")
```


Create Twitter [app](https://apps.twitter.com/) which will give access to: Consumer Key (API Key), Consumer Secret (API Secret), Access Token and Access Token Secret. 

```{r}
my_key <- 'ENTER YOUR KEY HERE'

my_secret <- 'ENTER YOUR SECRET HERE'

my_access_token <- 'ENTER YOUR ACCESS TOKEN HERE'

my_access_secret <- 'ENTER YOUR ACCESS SECRET HERE'
```


Set up the OAuth credentials for the twitteR session:

```{r}
setup_twitter_oauth(my_key, my_secret, my_access_token, my_access_secret)
```


The question should pop-up:
```
[1] "Using direct authentication"
Use a local file ('.httr-oauth'), to cache OAuth access credentials between R sessions?

1: Yes
2: No

Selection: 1
Adding .httr-oauth to .gitignore
```

Run Twitter search. In this case it is #BluePlanet2.

```{r}
#only max 600 due to image convert
tweets <- searchTwitter('BluePlanet2 -filter:retweets', n = 600)
#create dataframe
tweets.df <-twListToDF(tweets)
#look for users
userInfo <- lookupUsers(tweets.df$screenName) 
#create dataframe
userFrame <- twListToDF(userInfo)
#geolocate users
userFrame <- userFrame %>% 
  mutate(longlat = purrr::map(.$location, geocode))
#add the latitude and logitude values to dataframe
userFrame <- userFrame  %>% 
  unnest() 
#merge
merged <- merge(tweets.df, userFrame, by = "screenName")
```


Create the map: 

```{r}
world <- ggplot() +
  borders("world", colour = "#232227", fill = "#464648") +
  theme_map()

map <- world +
  geom_point(aes(x = lon, y = lat, frame = created.x, cumulative = TRUE),
             data = merged, colour = '#00FA9A', alpha = .7) +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "#232227")) 
```


Create the GIF image.

```{r}
library(gganimate)
library(animation)
ani.options(interval = 0.5)
gganimate(map, "blueplanet2.gif", ani.width = 600, ani.height = 400)
```
