---
title: "R Studio - Shiny"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: flatly
---

$~$

# Shiny app

Here is the basic set up for a Shiny app.

```{r}
library(shiny)

ui <- fluidPage()

server <- function(input, output) {}

shinyApp(ui = ui, server = server)
```

$~$

(**All these code examples can be used in R Studio: just start up the program, create a Single file (app.R), and copy and paste the code.**)

$~$

Let's create a basic map using Shiny. 

```{r message = FALSE}
library(shiny)
library(leaflet)

ui <- fluidPage(leafletOutput("map"))

server <- function(input, output, session) {
  
  output$map <- renderLeaflet({
    library(leaflet)
    leaflet() %>%
      addTiles()})}

shinyApp(ui, server)
```

$~$

# View and basemap

Let's change the basemap and set the view.

```{r message = FALSE}
library(shiny)
library(leaflet)

ui <- fluidPage(leafletOutput("mymap"))

server <- function(input, output, session) {
  
  output$mymap <- renderLeaflet({
    library(leaflet)
    leaflet() %>%
      setView(lng = -15, lat = 20, zoom = 1) %>%
      addTiles() %>%
      addProviderTiles(providers$Esri.WorldImagery)})}

shinyApp(ui, server)
```

$~$

# Marker

Using the example from the R Studio [section](https://marinespatialviz.github.io/marinespatialviz/rstudio.html#marker), let's add a marker. 

```{r message = FALSE}
library(shiny)
library(leaflet)

ui <- fluidPage(leafletOutput("mymap"))

server <- function(input, output, session) {
  
  output$mymap <- renderLeaflet({
    library(leaflet)
    leaflet() %>%
      addTiles() %>%
      setView(lng = 142, lat = 11, zoom = 3) %>%
      addMarkers(lng = 142.1999992, lat = 11.3499986) %>%
      addProviderTiles(providers$Esri.OceanBasemap)})}

shinyApp(ui, server)
```

$~$

## Pop-up marker

Let's add a pop-up to the marker. 

```{r message = FALSE}
library(shiny)
library(leaflet)

ui <- fluidPage(leafletOutput("mymap"))

server <- function(input, output, session) {
  
  output$mymap <- renderLeaflet({
    leaflet() %>%
    addTiles() %>%
    setView(lng = 142, lat = 11, zoom = 3) %>%
    addMarkers(lng = 142.1999992, lat = 11.3499986, popup = 'Mariana Trench') %>%
    addProviderTiles(providers$CartoDB.Positron)})}

shinyApp(ui, server)
```

$~$

## Circle marker

Change to marker to a circle marker. 

```{r message = FALSE}
library(shiny)
library(leaflet)

ui <- fluidPage(leafletOutput("mymap"))

server <- function(input, output, session) {
  
  output$mymap <- renderLeaflet({
    leaflet() %>%
    addTiles() %>%
    setView(lng = 142, lat = 11, zoom = 3) %>%
    addCircleMarkers(lng = 142.1999992, lat = 11.3499986, radius = 6, fillOpacity = .5, color = 'green') %>%
    addProviderTiles(providers$CartoDB.Positron)})}

shinyApp(ui, server)
```

$~$

## Costum marker

Let's add the submarine.

```{r message = FALSE}
library(shiny)
library(leaflet)

subIcon <- makeIcon(iconUrl = "https://image.flaticon.com/icons/png/512/190/190006.png",
                    iconWidth = 100, iconHeight = 95)

ui <- fluidPage(leafletOutput("mymap"))

server <- function(input, output, session) {
  
  output$mymap <- renderLeaflet({
    leaflet() %>%
    addTiles() %>%
    setView(lng = 142, lat = 11, zoom = 3) %>%
    addMarkers(lng = 142.1999992, lat = 11.3499986, icon = subIcon) %>%
    addProviderTiles(providers$CartoDB.Positron)})}

shinyApp(ui, server)
```

$~$

# Polyline

Let's add the Equator to the map. 

```{r message = FALSE}
library(shiny)
library(leaflet)

x = c(-180, 180)
y = c(0, 0)
e = data.frame(x, y)

ui <- fluidPage(leafletOutput("mymap"))

server <- function(input, output, session) {
  
  output$mymap <- renderLeaflet({
    library(leaflet)
    leaflet() %>%
      addTiles() %>%
      setView(lng = 0, lat = 0, zoom = 2) %>%
      addPolylines(lng = e$x, lat = e$y, color = "red") %>%
      addProviderTiles(providers$Esri.OceanBasemap)})}

shinyApp(ui, server)
```

$~$

#Polygon

Let's also highlight the tropics. 

```{r message = FALSE}
library(shiny)
library(leaflet)

x = c(-180, 180, 180, -180)
y = c(23.5, 23.5, -23.5, -23.5)
e = data.frame(x, y)

ui <- fluidPage(leafletOutput("mymap"))

server <- function(input, output, session) {
  
  output$mymap <- renderLeaflet({
    library(leaflet)
      leaflet() %>%
      addTiles() %>%
      setView(lng = 0, lat = 0, zoom = 2) %>%
      addPolygons(lng = e$x, lat = e$y, color = "orange", fillOpacity = .5) %>% 
      addProviderTiles(providers$Hydda.Base)})}

shinyApp(ui, server)
```
